Elaboration with First-Class Implicit Function Types

### 2020-02-23 paper.tex
stuff

%% %% alternative application infer
  %% &\einfer{t\,u}{ins}{\Theta_0}{\Gamma} :\equiv \edo \\
  %% &\quad (\Theta_1,\,\theta_1,\,t',\,A) \leftarrow \einfer{t}{\true}{\Theta_0}{\Gamma}\\
  %% &\quad \ecase\,\,A\,\,\eof\\
  %% &\qquad   ((x : A)\to B) \To \edo\\
  %% &\qquad\quad  (\Theta_2,\,\theta_2,\,u') \leftarrow
  %%                   \echeck{u}{\Theta_1}{(\Gamma[\theta_1])}{A}\\
  %% &\qquad\quad  \ereturn\,(\einsert{ins}{\Theta_2}{(\Gamma[\theta_1\circ\theta_2])}{(t'[\theta_2]\,u')}{(B[\theta_2][x\mapsto u'])})\\
  %% &\qquad A \To \fail\\
  %% &\einfer{t\,\{u\}}{ins}{\Theta_0}{\Gamma} :\equiv \edo \\
  %% &\quad (\Theta_1,\,\theta_1,\,t',\,A) \leftarrow \einfer{t}{\false}{\Theta_0}{\Gamma}\\
  %% &\quad \ecase\,\,A\,\,\eof\\
  %% &\qquad   (\{x : A\}\to B) \To \edo\\
  %% &\qquad\quad  (\Theta_2,\,\theta_2,\,u') \leftarrow
  %%                   \echeck{u}{\Theta_1}{(\Gamma[\theta_1])}{A}\\
  %% &\qquad\quad  \ereturn\,(\einsert{ins}{\Theta_2}{(\Gamma[\theta_1\circ\theta_2])}{(t'[\theta_2]\,\{u'\})}{(B[\theta_2][x\mapsto u'])})\\
  %% &\qquad A \To \fail\\

@@

We revisit now the $polyList$ example from Section \ref{sec:introduction}. We
assume the following:
\begin{alignat*}{3}
  & List && : \U \to \U \\
  & nil  && : \{A : \U\} \to List\,A\\
  & cons && : \{A : \U\} \to A \to List\,A
\end{alignat*}
In the following, we present a trace of checking $cons\,(\lambda\,x.\,x)\,nil$
at type $List\,(\{A : \U\}\to A \to A)$. We omit context and metacontext
parameters everywhere, and notate recursive calls by indentation. We also omit
some checking, inference, implicit insertion and unification calls which are not
essential for illustration.
\begin{alignat*}{3}
  & \scriptstyle{0 }\qquad\qquad\quad && \echeckt{cons\,(\lambda\,x.\,x)\,nil}{(List\,(\{A : \U\}\to A \to A))}\\
  & \scriptstyle{1 }  && \quad \einfert{cons\,(\lambda\,x.\,x)\,nil}{\true} \\
  & \scriptstyle{2 }  && \qquad \einfert{cons\,(\lambda\,x.\,x)}{\true}\\
  & \scriptstyle{3 }  && \qquad\quad \einfert{cons}{\true}\\
  & \scriptstyle{4 }  && \qquad\quad = cons\,\{\alpha_0\}\,:\,\alpha_0 \to List\,\alpha_0 \to List\,\alpha_0\\
  & \scriptstyle{5 }  && \qquad\quad \echeckt{\lambda\,x.\,x}{\alpha_0}\\
  & \scriptstyle{6 }  && \qquad\quad = \lambda\,x.\,x\\
  & \scriptstyle{7 }  && \qquad = cons\,\{\alpha_1 \to \alpha_1\}\,(\lambda\,x.\,x) : List\,(\alpha_1\to\alpha_1) \to List\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{8 }  && \qquad \echeckt{nil}{(List\,(\alpha_1\to\alpha_1))}\\
  & \scriptstyle{9 }  && \qquad = nil\,\{\alpha_1\to\alpha_1\}\\
  & \scriptstyle{10} && \quad = cons\,\{\alpha_1 \to \alpha_1\}\,(\lambda\,x.\,x)\,(nil\,\{\alpha_1\to\alpha_1\}): List\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{11} && \quad \unify\,(List\,(\{A : \U\}\to A \to A))\,(List\,(\alpha_1\to\alpha_1))\\
  & \scriptstyle{12} && \qquad \unify\,(\{A : \U\}\to A \to A)\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{13} && \qquad = \fail
\end{alignat*}

@@

\subsection{Handling Superfluous Implicit Functions}

Before we can move on to unification, checking and inference, we have to address
a curious issue. Assuming $Bool : \U$, $true : Bool$ and $false : Bool$,
consider the following surface expression:
\[
  \slet\,x : \_ = true\,\sin\,x
\]
What should this expression elaborate to? We would expect the result to be simply
\[
  \slet\,x : Bool = true\,\sin\,x
\]
However, there are infinitely many core terms which are conservative over the
surface expression in the sense of Theorem \ref{thm:conservativity}. That is, we
can wrap definitions with any number of implicit $\lambda$-s, and add implicit
applications accordingly to usage sites of the defined name. For example, we could have
\[
  \slet\,x : \{y : Bool\} \to Bool = \lambda\,\{y\}.\,true\,\sin\,x\,\{true\}
\]
This is clearly undesirable. With the type $\{y : Bool\} \to Bool$, the implicit
argument $y$ is never inferable, because the codomain type does not depend on
the domain, and the argument is never constrained. Hence, with the above
definition, we always have to write $x\,\{true\}$ or $x\,\{false\}$ when we want
to use $x$. In order to avoid such nonsense, we adopt the following principle:
\emph{elaboration should never invent non-dependent implicit function types.}

@@

\subsubsection{Algorithmic implementation of constraint solving}
The above specification for constancy constraints is compact but not
particularly algorithmic: we just magically get new definitional equalities
whenever we have constraints in contexts. In our prototype implementation, we
augment the unification procedure with eager removal of solvable constraints.

After solving a meta $\alpha$ during unification, which yields a unifying
$\theta$ substitution, we review all ($\constancy_{\Gamma,\,x : \Rec\,A}\,B$)
constraints in the context, such that $x$ occurs in $B$ inside a $\ol{t}$ spine
of some $\alpha\,\ol{t}$ term. In other words, we review constraints where the
new meta solution might make a difference.
\begin{enumerate}
  \item If we have $x \in \FreeVars(B[\theta])$, where $x$ occurs rigidly in
    $B[\theta]$, i.e.\ the occurrence is not in a spine of a meta, then no
    metasubstitution can possibly remove this occurrence. In this case the
    constraint holds vacuously, so we can use the rule
    \LabTirName{metasub/constancy} to return a $\theta'$ substitution which also
    solves the constraint.
  \item If we have $x \notin \FreeVars(B[\theta])$, we recursively unify
    $A[\theta]$ with $\epsilon$. If that succeeds, we get a $\theta'$ which
    unifies $A$ and $\epsilon$ and thus forces the constraint to hold, so we
    can again use \LabTirName{metasub/constancy} to solve the constraint.
  \item
    In any other case we simply return $\theta$ and keep the constraint around.
\end{enumerate}

@@

Now, let us assume that $B'$ is not an implicit function type and not
meta-headed. Then, we have the following case, where we solve a telescope domain
to be empty.
\begin{alignat*}{3}
& \unify_{\Theta_0|\Gamma}(\{x : \ol{A}\}\to B)\,B' :\equiv \edo\\
& \quad (\Theta_1,\,\theta_1) \leftarrow \unify_{\Theta_0|\Gamma}\,A\,\epsilon\\
& \quad \unify_{\Theta_1|\Gamma[\theta_1]}\,(B[\theta_1][x\mapsto[]])\,(B'[\theta_1])
\end{alignat*}
Again, we also have the symmetric case. For $\lambda\,\{x : \ol{A}\}.\,t$ and
$t\,\{u : \ol{A}\}$, unification is structural, and other cases remain the same
as in the the basic elaborator of Section \ref{sec:bidirectional_elaboration}.

@@

>>>>

@@

We revisit now the $polyList$ example from Section \ref{sec:introduction}. We
assume the following:
\begin{alignat*}{3}
  & List && : \U \to \U \\
  & nil  && : \{A : \U\} \to List\,A\\
  & cons && : \{A : \U\} \to A \to List\,A
\end{alignat*}
In the following, we present a trace of checking $cons\,(\lambda\,x.\,x)\,nil$
at type $List\,(\{A : \U\}\to A \to A)$. We omit context and metacontext
parameters everywhere, and notate recursive calls by indentation. We also omit
some checking, inference, implicit insertion and unification calls which are not
essential for illustration.
\begin{alignat*}{3}
  & \scriptstyle{0 }\qquad\qquad && \echeckt{cons\,(\lambda\,x.\,x)\,nil}{(List\,(\{A : \U\}\to A \to A))}
     \hspace{14em}\\
  & \scriptstyle{1 }  && \quad \einfert{cons\,(\lambda\,x.\,x)\,nil}{\true} \\
  & \scriptstyle{2 }  && \qquad \einfert{cons\,(\lambda\,x.\,x)}{\true}\\
  & \scriptstyle{3 }  && \qquad\quad \einfert{cons}{\true}\\
  & \scriptstyle{4 }  && \qquad\quad = cons\,\{\alpha_0\}\,:\,\alpha_0 \to List\,\alpha_0 \to List\,\alpha_0\\
  & \scriptstyle{5 }  && \qquad\quad \echeckt{\lambda\,x.\,x}{\alpha_0}\\
  & \scriptstyle{6 }  && \qquad\quad = \lambda\,x.\,x\\
  & \scriptstyle{7 }  && \qquad = cons\,\{\alpha_1 \to \alpha_1\}\,(\lambda\,x.\,x) : List\,(\alpha_1\to\alpha_1) \to List\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{8 }  && \qquad \echeckt{nil}{(List\,(\alpha_1\to\alpha_1))}\\
  & \scriptstyle{9 }  && \qquad = nil\,\{\alpha_1\to\alpha_1\}\\
  & \scriptstyle{10} && \quad = cons\,\{\alpha_1 \to \alpha_1\}\,(\lambda\,x.\,x)\,(nil\,\{\alpha_1\to\alpha_1\}): List\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{11} && \quad \unify\,(List\,(\{A : \U\}\to A \to A))\,(List\,(\alpha_1\to\alpha_1))\\
  & \scriptstyle{12} && \qquad \unify\,(\{A : \U\}\to A \to A)\,(\alpha_1\to\alpha_1)\\
  & \scriptstyle{13} && \qquad = \fail
\end{alignat*}

@@

\subsection{Handling Superfluous Implicit Functions}\label{sec:superfluous}

Before we can move on to unification and elaboration, we have to address
a curious issue. Assuming $Bool : \U$, $true : Bool$ and $false : Bool$,
consider the following surface expression:
\[
  \slet\,x : \_ = true\,\sin\,x
\]
What should this expression elaborate to? We would expect the result to be simply
\[
  \slet\,x : Bool = true\,\sin\,x
\]
However, there are infinitely many core terms which are conservative over the
surface expression in the sense of Theorem \ref{thm:conservativity}. That is, we
can wrap definitions with any number of implicit $\lambda$-s, and add implicit
applications accordingly to usage sites of the defined name. For example, we could have
\[
  \slet\,x : \{y : Bool\} \to Bool = \lambda\,\{y\}.\,true\,\sin\,x\,\{true\}
\]
This is clearly undesirable. With the type $\{y : Bool\} \to Bool$, the implicit
argument $y$ is never inferable, because the codomain type does not depend on
the domain, and the argument is never constrained. Hence, with the above
definition, we always have to write $x\,\{true\}$ or $x\,\{false\}$ when we want
to use $x$. In order to avoid such nonsense, we adopt the following principle:
\emph{elaboration should never invent non-dependent implicit function types.}

@@

\subsubsection{Algorithmic implementation of constraint solving}
\label{sec:algorithmic}
The above specification for constancy constraints is compact but not
particularly algorithmic: we just magically get new definitional equalities
whenever we have constraints in contexts. In our prototype implementation, we
implement eager removal of solvable constraints.

After solving a meta $\alpha$ during unification, which yields a unifying
$\theta$ substitution, we review all ($\constancy_{\Gamma,\,x : \Rec\,A}\,B$)
constraints in the context, such that $x$ occurs in $B$ inside a $\ol{t}$ spine
of some $\alpha\,\ol{t}$ term. In other words, we review constraints where the
new meta solution might make a difference.
\begin{enumerate}
  \item If we have $x \in \FreeVars(B[\theta])$, where $x$ occurs rigidly in
    $B[\theta]$, i.e.\ the occurrence is not in a spine of a meta, then no
    metasubstitution can possibly remove this occurrence. In this case the
    constraint holds vacuously, so we can use the rule
    \LabTirName{metasub/constancy} to return a $\theta'$ substitution which also
    solves the constraint.
  \item If we have $x \notin \FreeVars(B[\theta])$, we recursively unify
    $A[\theta]$ with $\epsilon$. If that succeeds, we get a $\theta'$ which
    unifies $A$ and $\epsilon$ and thus forces the constraint to hold, so we
    can again use \LabTirName{metasub/constancy} to solve the constraint.
  \item
    In any other case we simply return $\theta$ and keep the constraint around.
\end{enumerate}
Also, when we create a new constancy constraint, we immediately review it
as described above.

@@

Now, let us assume that $B'$ is not an implicit function type, curried function
type or meta-headed. Then, we have the following case, where we solve a
telescope domain to be empty.
\begin{alignat*}{3}
& \unify_{\Theta_0|\Gamma}(\{x : \ol{A}\}\to B)\,B' :\equiv \edo\\
& \quad (\Theta_1,\,\theta_1) \leftarrow \unify_{\Theta_0|\Gamma}\,A\,\epsilon\\
& \quad \unify_{\Theta_1|\Gamma[\theta_1]}\,(B[\theta_1][x\mapsto[]])\,(B'[\theta_1])
\end{alignat*}
Again, we also have the symmetric case. For $\lambda\,\{x : \ol{A}\}.\,t$ and
$t\,\{u : \ol{A}\}$, unification is structural, and other cases remain the same
as in the the basic elaborator of Section \ref{sec:bidirectional_elaboration}.

@@

In the definition of checking, we insert a new clause after
$\echeck{t}{\Theta}{\Gamma}{(\{x : A\}\to B)}$:
\begin{alignat*}{3}
& \echeck{t}{\Theta_0}{\Gamma}{(\alpha\,\ol{t})} :\equiv \edo\\
& \quad (\Theta_1,\,\theta_1,\,A) \leftarrow \freshMeta{\Theta_0}{\Gamma}{\Tel}\\
& \quad (\Theta_2,\,\theta_2,\,t',\,B) \leftarrow \einfer{t}{\true}{\Theta_1}{\Gamma[\theta_1],\,x:\Rec\,A}\\
& \quad (\Theta_3,\,\theta_3) \leftarrow \newConstancy{\Theta_2}{\Gamma[\theta_{12}]}{x}{(A[\theta_2])}{B}\\
& \quad (\Theta_4,\,\theta_4) \leftarrow
            \unify\, ((\alpha\,\ol{t})[\theta_{123}])\,(\{x : \ol{A[\theta_{23}]}\} \to B[\theta_3])\\
& \quad \ereturn\,(\Theta_4,\,\theta_{1234},\,(\lambda\,\{x : \ol{A[\theta_{234}]}\}.\,t'[\theta_{34}]))
\end{alignat*}
Hence, when checking a term with a meta-headed type, we create a fresh meta with
$\Tel$ type, infer a type for the term, and wrap the result in a strictly
curried $\lambda$. We again need to create new constancy constraint. This way,
if $B$ does not depend on $x : \Rec\,A$, the strictly curried $\lambda$ in the
output immediately computes away, since $A$ is solved to $\epsilon$.

This concludes the definition of the extended elaborator. The new algorithm is
sound with respect to the extended core syntax, and it also has the
conservativity property from Theorem \ref{thm:conservativity} if we additionally
allow elaboration to insert $\lambda$-s for strictly curried functions. We present
some examples of the algorithm at action.

\begin{example}
We return to the $polyList$ example from Section \ref{sec:issues}. We trace
elaboration using the extended algorithm.
\begin{alignat*}{3}
  & \scriptstyle{0 }\qquad\qquad && \echeckt{cons\,(\lambda\,x.\,x)\,nil}{(List\,(\{A : \U\}\to A \to A))}
      \hspace{14em}\\
  & \scriptstyle{1 }  && \quad \einfert{cons\,(\lambda\,x.\,x)\,nil}{\true} \\
  & \scriptstyle{2 }  && \qquad \einfert{cons\,(\lambda\,x.\,x)}{\true}\\
  & \scriptstyle{3 }  && \qquad\quad \einfert{cons}{\true}\\
  & \scriptstyle{4 }  && \qquad\quad = cons\,\{\alpha_0\}\,:\,\alpha_0 \to List\,\alpha_0 \to List\,\alpha_0\\
  & \scriptstyle{5 }  && \qquad\quad \echeckt{\lambda\,x.\,x}{\alpha_0}\\
  & \scriptstyle{6 }  && \qquad\quad = \lambda\,\{y : \ol{\alpha_1}\}.\,\lambda\,x.\,x\\
  & \scriptstyle{7 }  && \qquad = cons\,
                       \{\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}\}\,
                       (\lambda\,\{y : \ol{\alpha_1}\}.\,\lambda\,x.\,x)\\
  & \scriptstyle{8 }  && \qquad \echeckt{nil}{(List\,(\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}))}\\
  & \scriptstyle{9 }  && \qquad = nil\,\{\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}\}\\
                       & \scriptstyle{10} && \quad = cons\,\{\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}\}\,(\lambda\,\{y : \ol{\alpha_1}\}.\,\lambda\,x.\,x)\,\\
                       & && \hspace{4.4em} (nil\,\{\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}\})\\
  & && \hspace{3em} : List\,(\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\})\\
  & \scriptstyle{11} && \quad \unify\,(List\,(\{A : \U\}\to A \to A))\,(List\,(\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\}))\\
  & \scriptstyle{12} && \qquad \unify\,(\{A : \U\}\to A \to A)\,(\{y : \ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y : \ol{\alpha_1}\})\\
  & \scriptstyle{13} && \qquad\quad \unify\,\alpha_1\,((A : \U) \TCons (\alpha_3\,A))\\
  & \scriptstyle{14} && \qquad \quad \unify\,(A \to A)\,(\{z : \ol{\alpha_3\,A}\} \to \alpha_2\,\{A\}\,\{z : \ol{\alpha_3\,A}\}\to \alpha_2\,\{A\}\,\{z : \ol{\alpha_3\,A}\})\\
  & \scriptstyle{15} && \qquad \qquad \unify\,(\alpha_3\,A)\,\epsilon\\
  & \scriptstyle{16} && \qquad \qquad \unify\,(A \to A)\,(\alpha_2\,\{A\} \to \alpha_2\,\{A\})\\
  & \scriptstyle{17} && \qquad \qquad \quad \unify\,A\,(\alpha_2\,\{A\})\\
  & \scriptstyle{18} && \qquad \qquad \quad \unify\,A\, A\\
  & \scriptstyle{19} && = cons\,\{\{A : \U\}\to A \to A\}\,(\lambda\,\{A\}\,x.\,x)\,(nil\,\{\{A : \U\}\to A \to A\})
\end{alignat*}
We diverge from the previous attempt at line $\scriptstyle{5}$. Here, we check
$\lambda\,x.\,x$ with the meta $\alpha_0$, so we create a fresh $\alpha_1 :
\Tel$ meta and wrap the result as $\lambda\,\{y :
\ol{\alpha_1}\}.\,\lambda\,x.\,x$. This result has the inferred type $\{y :
\ol{\alpha_1}\} \to \alpha_2\,\{y : \ol{\alpha_1}\}\to \alpha_2\,\{y :
\ol{\alpha_1}\}$, and we promptly unify $\alpha_0$ (which stands for the list
element type) with it. On line $\scriptstyle{10}$, we return the elaborated
$cons$ expression, where the list element type is made explicit. It only remains
to unify the inferred and expected types. On line $\scriptstyle{12}$ we have the
case where a curried function type is matched with an implicit function type, so
on line $\scriptstyle{13}$ we refine $\alpha_1$ to a non-empty telescope, and
proceed unifying the domains. Note that on line $\scriptstyle{14}$ we have
$\alpha_2\,\{A\}\,\{z : \ol{\alpha_3\,A}\}$, which results from applying the
substitution $y \mapsto (A :: z)$, and computing $\alpha_2\,\{(A :: z) : \ol{(A :
  \U) \TCons (\alpha_3\,A)}\}$ further using the \LabTirName{app-$\TCons$} rule
from Figure \ref{fig:telescopes}.

On line $\scriptstyle{14}$ we have the case when a curried function type is
matched with a type which is not a curried function, implicit function or a
meta-headed type. We accordingly unify domain telescope $\alpha_3\,A$ with
$\epsilon$, which causes $\alpha_3$ to be solved as $\lambda\,A.\,\epsilon$
according to standard pattern unification. Now, $\alpha_2\,\{A\}\,\{z :
\ol{\alpha_3\,A}\}$ computes to $\alpha_2\,\{A\}\,\{z : \epsilon\}$, which
further computes to $\alpha_2\,\{A\}$ by \LabTirName{app-$\epsilon$}. From here,
unification finishes with success. On the last line, the expected output is
returned: since the $\alpha_1$ telescope meta is now solved, curried function
types and abstractions are computed away.
\end{example}

\begin{example}
We illustrate now the action of constancy constraints, using the example from
Section \ref{sec:superfluous}. Again, assume $Bool : \U$ and $true : Bool$.
\begin{alignat*}{3}
& \scriptstyle{0}\qquad\qquad && \einfert{\slet\,x : \_ = true\,\sin\,x}{\true}
      \hspace{21em}\\
& \scriptstyle{1} && \quad \echeckt{\_}{\U}\\
& \scriptstyle{2} && \quad = \alpha_0\\
& \scriptstyle{3} && \quad \echeckt{true}{\alpha_0}\\
& \scriptstyle{4} && \qquad \mathsf{freshMeta}\,\Tel\\
& \scriptstyle{5} && \qquad = \alpha_1\\
& \scriptstyle{6} && \qquad \einfert{true}{\true}\\
& \scriptstyle{7} && \qquad = true : Bool\\
& \scriptstyle{8} && \qquad \mathsf{newConstancy}_{\emptycon,\,x : \Rec\,\alpha_1}\,Bool\\
& \scriptstyle{9} && \qquad\quad \unify\,\alpha_1\,\epsilon\\
& \scriptstyle{10} && \qquad \unify\,\alpha_0\,Bool\\
& \scriptstyle{11} && \quad = true\\
& \scriptstyle{12} && \quad \einfert{x}{\true}\\
& \scriptstyle{13} && \quad = true : Bool\\
& \scriptstyle{14} && = (\slet\,x : Bool = true\,\sin\,x) : Bool
\end{alignat*}
First we create a fresh meta $\alpha_0$ for the hole on line $\scriptstyle{2}$,
then we check $\true$ with it. Since we are checking with a meta-headed type, we
create a fresh telescope meta $\alpha_1$, then infer $Bool$ for $true$. On line
$\scriptstyle{8}$ we create a constancy constraint, and immediately try to solve
it, in accordance with the algorithmic implementation in Section
\ref{sec:algorithmic}. Since $Bool$ does not depend on the domain, we solve the
constraint and thereby solve $\alpha_1$ as $\epsilon$. Hence, we simply return
$true$ on line $\scriptstyle{11}$, since $\lambda\,\{x : \ol{\epsilon}\}.\,true$
computes to that, and elaboration succeeds with the expected output.
\end{example}
